Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-09-24 edubots_surveys.Rnw
Update edubots_surveys.Rnw

Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp,
Telegram and Facebook Messenger took place. Some messaging applications have
built-in chatbots to support a synchronous conversation between the different
parties \cite{differ.chat}, while other chatbots are developed as standalone
systems and can possibly be attached to a messaging application using an API
(Application Program Interface).

A \textit{chatbot} is a program, sometimes developed using Artificial
Intelligence techniques, able to communicate in a similar way as humans do
\cite{Gong2008}, using, in some cases, natural language. Indeed, most of these
applications would be, apparently, close to passing a classic Turing test
\cite{moor2003turing}, since they are able to answer almost any question
fluently, and even pose own questions in their conversations. The recent
advancement in this discipline has played an important role in many fields
especially in education and online tutoring
\cite{clarizia2018,Smutny2020}. These automatic systems facilitate the delivery
of personalized learning by adapting to students’ pace of learning and providing
customized online tutoring outside the classroom. Thus, chatbots can
significantly contribute to providing interactive learning experiences as well
as improving individual attention \cite{agarwal2020}.  In this sense, chatbot
technology offers a great opportunity for the improvement of tutoring systems
\cite{Daniel2016,agarwal2020}, as not all students are comfortable with
face-to-face tutoring with the instructor. In fact, in many cases, some students
experience stress because of their need to ask a question in front of the entire
class. This is why many students resort to silence in the classroom and tend to
contact their teachers later via email.  Consequently, this can lead to not only
a delay in obtaining answers to their questions but can also cause a significant
increase in their teachers’ workload, especially when factoring in the
disproportion between the class size and the number of teachers. Hence, the
chatbot technology has a potential to mitigate this problem by providing answers
to students’ questions and facilitating a dynamic and autonomous learning
experience \cite{Griol2014,kim2020}. In addition, using an automated system such
as a chatbot, can draw teachers’ attention to topics that students struggle to
comprehend or need further assistance in understanding.

>>>>

\textcolor{blue}{In the last years, messaging applications such as WhatsApp or Telegram are being used in teaching scenarios mainly at secondary and higher education.
In addition to their main use, some of these tools offer the possibility of interact with \textit{chatbots} (or just bots), even supporting synchronous conversation between the different
parties \cite{differ.chat}. There is also possible to create a standalone chatbot application and attach it to a messaging tool through an API (Application Program Interface).}

\textcolor{blue}{\textit{chatbots} are autonomous agents able to communicate and interact with humans (or other chatbots) in a huma-like way \cite{Gong2008}, answering question and even posing their own ones to the user. 
Thus, we can say that they are close to passing a Turing Test \cite{moor2003turing}. They are implemented by means of different Artificial Intelligence techniques, such as natural language processing.
Inside the plethora of possible applications of chatbots, education is one of the most prolific nowadays \cite{clarizia2018,Smutny2020}. In this domain, they facilitate the so-called 
\textit{personalized learning}, i.e. they adapt themselves to students’ pace of learning and provide online tutoring outside the classroom, which have been proved to be very effective increasing their 
engagement and participation in the subjects \cite{agarwal2020}. Moreover chatbots' tutoring possibilities aid to reduce the stress of students \cite{Daniel2016,agarwal2020} by avoiding the face-to-face tutoring with their teacher, 
or asking questions in front of the class. 
}

This is why many students resort to silence in the classroom and tend to
contact their teachers later via email.  Consequently, this can lead to not only
a delay in obtaining answers to their questions but can also cause a significant
increase in their teachers’ workload, especially when factoring in the
disproportion between the class size and the number of teachers. Hence, the
chatbot technology has a potential to mitigate this problem by providing answers
to students’ questions and facilitating a dynamic and autonomous learning
experience \cite{Griol2014,kim2020}. In addition, using an automated system such
as a chatbot, can draw teachers’ attention to topics that students struggle to
comprehend or need further assistance in understanding.
